KIN: A method to infer relatedness from low-coverage ancient DNA

### 2022-08-18 paper_overleaf/main.tex
some naming issue

\begin{figure}[h!]
    \includegraphics[width=18cm]{plots/inkscape_finalImg/schematic_sib_rev.png}
    \centering
    \caption{IBD sharing between siblings without and with runs of homozygosity (ROH). In top row, recombined chromosomes inherited from parents by a pair of siblings are shown. On the left, the parents have unrelated chromosomes, and on the right one parent has a homozygous pair of chromosomes. The bottom row shows the expected proportion of differences ($p$) along the chromosome. In both cases, $p$ can take values of $p_0$, $p_1$ or $p_2$, which are the expected proportion of differences in IBD states 0,1 and 2, respectively.  }
    \label{fig0:schematic}
\end{figure}

>>>>

\begin{figure}[h!]
    \includegraphics[width=18cm]{plots/inkscape_finalImg/schematic_sib_rev.png}
    \centering
    \caption{IBD sharing between siblings without and with runs of homozygosity (ROH). (A) Schematic of chromosomes for parent 1 (Par1)and parent 2 (Par2). On the left, the parents have unrelated chromosomes depicted with different colors, and on the right parent 1 has a homozygous pair of chromosomes. (B) In top row, recombined chromosomes inherited from parents by a pair of siblings are shown. The bottom row shows the expected proportion of differences ($p$) along the chromosome. In both cases, $p$ can take values of $p_0$, $p_1$ or $p_2$, which are the expected proportion of differences in IBD states 0,1 and 2, respectively.  }
    \label{fig0:schematic}
\end{figure}
